---
title: "Strava-flex"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
    vertical_layout: fill
    source_code: https://github.com/rafaelschlatter/strava-flex
    social: menu
---

```{r setup, include=FALSE}
source("install_packages.R")

strava_keys = fromJSON('keys.json')$strava
strava_goals = fromJSON('keys.json')$goals
strava_athlete = fromJSON("keys.json")$athlete
stoken <- httr::config(token = strava_oauth(strava_keys$app_name,
                                            strava_keys$client_id,
                                            strava_keys$client_secret,
                                            app_scope = 'view_private'))

activities <- get_activity_list(stoken)
athlete <- get_athlete(stoken)
df <- compile_activities(activities)
df$row <- seq.int(nrow(df))
df$calendar_date <- as.Date(df$start_date)
df$calendar_year <- lubridate::year(df$start_date)
df$calendar_month <- lubridate::month(df$start_date)
df$calendar_week <- lubridate::week(df$start_date)
df$weekday <- weekdays(as.Date(df$start_date))
df$month <- month.name[df$calendar_month]

y_2018 <- subset(df, calendar_date > as.Date("2017-12-31") & calendar_date < as.Date("2018-12-31"))
y_2019 <- subset(df, calendar_date > as.Date("2018-12-31"))
yearly_activites <- y_2019

remove_latlng <- function(stream) {
  for (i in seq(length(stream))) {
    if (toString(stream[[i]]["type"]) == "latlng") {
      stream[[i]] <- NULL
      break
    }
  }
  return(stream)
}

stream_to_df <- function(stream) {
  for (i in seq(length(stream))) {
    column_name = toString(stream[[i]]["type"])
    column_data = unlist(stream[[i]]["data"])
    if (i == 1) {
      df <- data.frame(column_name=column_data)
    }
    else {
      df[column_name]<-column_data
    }
  }
  return(df)
}

get_latest_activity <- function(df, workout_type) {
  type_activities <- df[df$type == workout_type, ] 
  latest_id <- type_activities["id"][1, ]
  return(latest_id)
}

run_latest_id <- get_latest_activity(yearly_activites, "Run")
run_stream <- get_streams(stoken, id = run_latest_id)
run_stream_clean <- remove_latlng(run_stream)
run_stream_df <- stream_to_df(run_stream_clean)

calculate_max_heartrate <- function(birthdate) {
  age <- round((as.numeric(Sys.Date() - as.Date(birthdate)) / 365))
  return(220-age)
}

calculate_heartrate_zone <- function(max_hr, hr_data) {
  breaks <- c(0.5*max_hr, 0.6*max_hr, 0.7*max_hr, 0.8*max_hr, 0.9*max_hr, 1*max_hr)
  lables <- c("Very light", "Light", "Moderate", "Intense", "Maximum")
  bins <- cut(hr_data, breaks = breaks, include.lowest = TRUE, right = FALSE, labels = lables)
  return(bins)
}
```

Sidebar {.sidebar}
=======================================================================
### Athlete Information
**First name**: `r athlete$firstname`  
**Last name**: `r athlete$lastname`  
**City**: `r athlete$city`  
**Country**: `r athlete$country`  

**Latest activity**: `r yearly_activites[1,]$calendar_date`

### All-time Statistics
**Distance**: `r round(sum(df$distance))`km  
**Activity time**: `r round(sum(df$elapsed_time) / (60*60), 2)`hrs  
**Number of activities**: `r length(df$id)`

Year-to-date statistics
=======================================================================
Row {data-height = 350}
-----------------------------------------------------------------------
### Yearly goal
Your current yearly km goal is set to `r strava_goals$yearly_km`km.
```{r}
current_distance = round(sum(yearly_activites$distance), digits = 1)

first = strava_goals$yearly_km / 3
second = first * 2

gauge(current_distance, min = 0, max = strava_goals$yearly_km, symbol = 'km', gaugeSectors(
  success = c(second+1, strava_goals$yearly_km), warning = c(first+1, second), danger = c(0, first)
))
```

### Weekly activity minutes
Your current weekly activity goal is set to `r strava_goals$weekly_min` min.  
```{r}
current_date <- Sys.Date()
current_day <- weekdays(current_date)

if (current_day == "Monday") {
  weekstart <- current_date
} else if (current_day == "Tuesday") {
  weekstart <- current_date - 1
} else if (current_day == "Wednesday") {
  weekstart <- current_date - 2
} else if (current_day == "Thursday") {
  weekstart <- current_date - 3
} else if (current_day == "Friday") {
  weekstart <- current_date - 4
} else if (current_day == "Saturday") {
  weekstart <- current_date - 5
} else {
  weekstart <- current_date - 6
}

weekly_activites = subset(df, calendar_date > weekstart)
weekly_min = round(sum(weekly_activites$elapsed_time) / 60)

first = strava_goals$weekly_min / 3
second = first * 2

gauge(weekly_min, min = 0, max = strava_goals$weekly_min, symbol = 'min', gaugeSectors(
  success = c(second+1, strava_goals$weekly_min), warning = c(first+1, second), danger = c(0, first)
))
```

### Activities by type
```{r}
activity_types <- as.data.frame(yearly_activites$type)
colnames(activity_types) <- "type"
activity_types$type <- factor(activity_types$type)

tooltip <- JS("function(){
  return this.point.name + ':<br/>' +
  this.y + ' activities<br/>' +
  Highcharts.numberFormat(this.percentage, 2) + '%<br />';
}")

hc <- highchart() %>% 
  hc_chart(type = "pie") %>% 
  hc_add_series(name = "Activity type", data = activity_types$type, dataLabels = list(enabled = TRUE)) %>%
  hc_yAxis(categories = c(activity_types$type)) %>%
  hc_tooltip(formatter = tooltip) %>%
  hc_add_theme(hc_theme_google())
hc
```

Row {data-height = 650}
-----------------------------------------------------------------------
### Monthly distance (all activity types)
```{r}
monthly_dist <- group_by(yearly_activites, month, type) %>% summarize(dist = sum(distance))
monthly_dist_wide <- spread(monthly_dist, type, dist)
monthly_dist_wide$month <- factor(monthly_dist_wide$month, levels = month.name)
monthly_dist_wide <- monthly_dist_wide[order(monthly_dist_wide$month), ]


hc <- highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_plotOptions(column = list(
    stacking = "normal")
  ) %>% 
  hc_xAxis(categories = monthly_dist_wide$month) %>% 
  hc_yAxis(min = 0, title = list(text = "Total distance in km"),
           plotLines = list(
                 list(
                   label = list(text = "Goal"),
                   color = "red",
                   width = 2,
                   value = strava_goals$montly_km
                   )
                 )) %>%
  hc_series(list(name = "Running (km)", data = monthly_dist_wide$Run),
            list(name = "Nordic Ski (km)", data = monthly_dist_wide$NordicSki))  %>%
  hc_add_theme(hc_theme_google())
hc
```

### Activity heatmap
```{r}
heatmap_data <- group_by(yearly_activites, calendar_week, weekday) %>% summarize(dist = sum(distance))
heatmap_data$weekday <- factor(heatmap_data$weekday, levels = c("Monday", "Tuesday", "Wednesday",
                                                                "Thursday", "Friday", "Saturday", "Sunday"))

tooltip <- JS("function(){
  return 'Week ' + this.point.x + ', ' +  this.series.yAxis.categories[this.point.y] + ':<br>' +
  'Distance: ' + Highcharts.numberFormat(this.point.value, 2) + 'km';
}")

hc <- hchart(heatmap_data, "heatmap", hcaes(x = calendar_week, y = weekday, value = dist)) %>%
  hc_xAxis(title = list(text = "Calendar week")) %>%
  hc_colorAxis(stops = color_stops(10, rev(RColorBrewer::brewer.pal(10, "RdBu")))) %>%
  hc_tooltip(formatter = tooltip) %>%
  hc_add_theme(hc_theme_google())
hc
```


Last activity
=======================================================================
Row {data-height=600}
-----------------------------------------------------------------------
### Lastest activity
```{r}
hc <- highchart() %>% 
  hc_chart(type = "line") %>%
  hc_xAxis(title = list(text = "Distance in meters")) %>%
  hc_yAxis_multiples(
    list(title = list(text = "Heartrate / Cadence"), min=0, max=200),
    list(title = list(text = "Altitude"), min=0, max=600, opposite = TRUE)
  ) %>% 
  hc_add_series(yAxis=1, run_stream_df, "area", hcaes(x=distance, y=altitude),
                name = "Altitude", color = "gray") %>%
  hc_add_series(yAxis=0, run_stream_df, "line", hcaes(x=distance, y=heartrate), name = "Heartrate") %>%
  hc_add_series(yAxis=0, run_stream_df, "line", hcaes(x=distance, y=cadence), name = "Cadence") %>%
  hc_tooltip(sort = TRUE, table = TRUE) %>%
  hc_add_theme(hc_theme_google())
hc
```

Row {data-height=400}
-----------------------------------------------------------------------
### Activity info
```{r}
```

### Heart rate zones
```{r}
hr_data <- run_stream_df$heartrate
max_hr <- calculate_max_heartrate(strava_athlete$birthdate)
hr_zones = calculate_heartrate_zone(max_hr, run_stream_df$heartrate)

hc <- highchart() %>%
  hc_chart(type = "column") %>% 
  hc_xAxis(categories = levels(hr_zones)) %>%
  hc_yAxis(title = list(text = "Heartrate"))
  hc_add_series(hr_zones,
                showInLegend = FALSE,
                colorByPoint = TRUE,
                colors = c("blue", "green", "yellow", "orange", "red")) %>%
  hc_plotOptions(groupPadding = 0) %>%
  hc_add_theme(hc_theme_google())
hc
```